---
output: html_document
---

Getting set up for MEES614  
========================================================
***

### R

As the name of the course implies, we will use R for all coursework. Download and install the latest version of [R](http://cran.r-project.org/) for your platform. 

### RStudio

Download and install [RStudio](http://www.rstudio.com/). You want the **desktop** version for your platform.

### Stypi

We will use [Stypi](https://code.stypi.com) to facilitate live, collaborative coding. Please visit the [site](https://code.stypi.com) and create a user account. When you are done email your Stypi username to me: <mfitzpatrick@al.umces.edu>. 

### GitHub

We will use GitHub to track versions of our R scripts and to turn in homework assignments. There are multiple steps for setting up your GitHub account for use in this course, as follows:

1. Setup a [GitHub Education account](https://education.github.com/). You'll want a **Student / Individual** account found by clicking on "Request a discount".
2. Create the following *repositories* (places where you will store your files).
  + For homework and other assignments that only I can see, create a **private** GitHub repository named `mees614-2015-UID-hw`, replacing "UID" with your UID.
      + Add me as a collaborator to your **private** repository.
        + [Matt Fitzpatrick: fitzLab-AL](https://github.com/fitzLab-AL)
  + For group work that anyone can access, create a **public** GitHub repository named `mees614-2015-lastname-firstname` using your name.
3. *Clone* both your **private** and **public** repository to your personal computer.
4. Within your **private** repository (the one named `mees614-2015-UID-hw`), create a folder named `hw1`. 

### R Markdown

There's nothing to install or signup for to use R Markdown, which comes with RStudio, but you'll need to read up on R Markdown as you will code your assignments in R and *author* them in R Markdown. You will use GitHub to submit your R Markdown documents to me. You can learn more about R Markdown [here](http://rmarkdown.rstudio.com/). 




When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r}
summary(cars)
```

You can also embed plots, for example:

```{r, echo=TRUE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
