---
output: html_document
---

Getting set up for MEES614  
========================================================
***

## Software & User Accounts

### R

As the name of the course implies, we will use R for all coursework. Because knowing basic R is a prerequisite for registering for this course, you should not need to download and install the latest version of [R](http://cran.r-project.org/) for your system...unless you just bought a new computer. 

### Git & GitHub

Git is a file version control system and GitHub is an online Git resource for coding-based projects. We will use GitHub to track versions of our R scripts and to turn in homework assignments. There are multiple steps for setting up Git and GitHub for use in this course, as follows:

1. Download and install [Git](http://git-scm.com/) for your system. Git interfaces with RStudio (see below), but needs to be installed first.
2. Setup a [GitHub Education account](https://education.github.com/). You'll want a **Student / Individual** account found by clicking on "Request a discount".
3. Using your newly created Git account, create the following *repositories* (places where you will store your files on GitHub and, eventually, your local computer).
  + For homework and other assignments that only I can see, create a **private** GitHub repository named `mees614-2015-UID`, replacing "UID" with your UID.
      + Add me as a collaborator to your **private** repository.
        + [Matt Fitzpatrick: fitzLab-AL](https://github.com/fitzLab-AL)
  + For group work that anyone can access, create a **public** GitHub repository named `mees614-2015-lastname-firstname` using your name.
4. *Clone* both your **private** and **public** repositories to your personal computer.
5. Within the newly cloned **private** repository (the one named `mees614-2015-UID`) on your machine, create a folder named `hw1`.

### RStudio

RStudio is a powerful and productive user interface for R that integrates scripting, running those scripts in R, plotting, help files, and Git. Download and install [RStudio](http://www.rstudio.com/). You want the **desktop** version for your system.

### Stypi

We will use [Stypi](https://code.stypi.com) to facilitate live, collaborative coding. Please visit the [site](https://code.stypi.com) and create a user account. When you are done, email your Stypi username to me: <mfitzpatrick@al.umces.edu>. 

## Completing & Submitting Homework

### Authoring HW using R Markdown

R Markdown comes with RStudio, but you will need to install a few packages the first time you use (RStudio will do this automatically for you). You will code your assignments in R and *author* them in R Markdown. You will use GitHub to submit your R Markdown documents to me. You can learn more about R Markdown [here](http://rmarkdown.rstudio.com/). BTW - this document was created using R Markdown.

* Author your homework using R Markdown. The raw file should be saved (by default) with a `.rmd` extension.
* As you work, "commit" your `.rmd` file to your private GitHub directory.
* Once complete, compile your homework to an HTML document using Rstudio's `Knit HTML` button. This will produce a new, formatted document with `.html` extension.

### Steps for submitting HW using GitHub

1. Check that you have commited all the files associated with your HW assignment to your local Git repository. This may include more than just the `.html` file. For examples, figures a placed in a`/figures` subdirectory






When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r}
summary(cars)
```

You can also embed plots, for example:

```{r, echo=TRUE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
